Holomorphic field theories and higher algebra

### 2024-09-26 draft.tex
just making sure it is all up to date

A confession is necessary here, because this replacement is a bit misleading.
The holomorphic version of the model case, known as the free $\beta\gamma$ system,
actually has holomorphic maps into $T^* \CC^n$ as the space of solutions.
The algebraic maps are precisely $T^* \CC^n$-valued Laurent polynomials.
\footnote{One can extract the algebraic model from the holomorphic model by taking formal power series expansions at the level of observables.}

>>>>

A confession is necessary here, because this replacement is a bit misleading.
The holomorphic version of the model case, known as the free $\beta\gamma$ system,
actually has holomorphic maps into $T^* \CC^n$ as the space of solutions.
The algebraic maps are precisely $T^* \CC^n$-valued Laurent polynomials.\footnote{One can extract the algebraic model from the holomorphic model by taking formal power series expansions at the level of observables.}
